# Some Final Thoughts

## Marathon Kids

### Mean and correlation Results

```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(datasauRus)
library(dplyr)
library(ggplot2)
data("datasaurus_dozen")
q1 <- datasaurus_dozen %>% 
  group_by(dataset) %>% 
  summarise(mean(x), mean(y), cor(x,y))
knitr::kable(q1)
```


### A picture is worth a thousand words (or a dinosaur)

```{r, echo=FALSE, warning=FALSE, message=FALSE}
ggplot(datasaurus_dozen, aes(x = x, y = y)) +
  facet_wrap(~ dataset, nrow = 3) +
  geom_point()
```

### Reference

Same Stats, Different Graphs: Generating Datasets with Varied Appearance and Identical Statistics through Simulated Annealing.  Matejka,  Fitzmaurice. Proceedings of the 2017 CHI Conference on Human Factors in Computing Systems. May 2017 Pages 1290–1294 https://doi.org/10.1145/3025453.3025912.

## Starwars

### Missing values by variable

```{r, echo=FALSE, warning=FALSE, message=FALSE}

library(dplyr)
data("starwars")
q1 <- starwars %>% select(name, height, mass, homeworld, birth_year, species) 
q2 <-  q1 %>%
  summarise_all(funs(sum(is.na(.))))
knitr::kable(q2)
```

### BMI summary

```{r, echo=FALSE, warning=FALSE, message=FALSE}
starwars <- starwars %>% select(name, height, mass, homeworld) %>% na.omit() %>% 
  mutate(BMI = mass/(height)^2*10000)
knitr::kable(head(starwars))
q7 <- starwars %>% summarise(mean_bmi = mean(BMI), median_bmi = median(BMI), max_bmi = max(BMI), min_bmi = min(BMI))
knitr::kable(q7)
```

### Top contenders...

```{r, echo=FALSE, warning=FALSE, message=FALSE}
starwars <- starwars %>%
  group_by(homeworld) %>% 
  mutate(avg_bmi_by_hw = mean(BMI)) %>% 
  ungroup()


above_avg_BMI <- starwars %>%
  filter(BMI > starwars$avg_bmi_by_hw) %>%
  group_by(homeworld) %>%
  summarise(count = n()) %>%
  arrange(desc(count))
head(above_avg_BMI, 7)
```

### And the winners are...

```{r, echo=FALSE, warning=FALSE, message=FALSE}
above_avg_BMI[1:2,]

```

### NFL, one option

[Just one person's thoughts](https://rpubs.com/afuecker/727520)

